Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-10 podc16/paper2.tex
c-struct and notation

We consider a set of processes $P$ subject to crash-stop faults and communicating by message-passing in an asynchronous network.
We also consider a deterministic state-machine $M$ whose set of commands is $C$. 
We say that two commands $c_a$, $c_b$ \textit{commute} if executing $c_a$ before $c_b$ has the same effect on the state machine as executing $c_b$ before $c_a$. We assume that a command does not commute with itself.
We also consider a symmetric relation $R \subseteq C\times C$, called \textit{dependency relation}, such that: for any command $c$, $\left( c,c \right)\notin R$, and if $\left( c_a,c_b \right)\notin R$ then $c_a$ and $c_b$ commute.

\subsection{Computing Dependency-Sets}

A dependency-set computation algorithm exposes the input actions ${\operatorname{announce}\left( c \right)}^p$, where $c$ is a command, and the output actions ${suggest\left( c, d \right)}^p$, where $c$ is a command and $d$ is a set of commands.
Moreover, a dependency-set computation algorithm must ensure that:
\begin{enumerate}[noitemsep,nolistsep]
    \item For any suggestion ${suggest\left( c, d \right)}^p$, every command in $\{c\}\cup d$ must have been announced before.
    \item For any two suggestions ${suggest\left( c_1, d_1 \right)}^p$ and ${suggest\left( c_2, d_2 \right)}^p$,  if $c_1$ and $c_2$ do not commute (i.e., $\left( c_1,c_2 \right) \in R$) then either $c_1\in d_2$ or $c_2 \in d_1$.
\end{enumerate}

@@

\subsection{Agreeing on Dependency Sets}

>>>>

We consider a set of processes $P$ subject to crash-stop faults and communicating by message-passing in an asynchronous network. Processes in $P$ must solve the Generalized Consensus problem~\cite{lamport-generalized}. Each process receives proposals for commands of the form \texttt{Propose}$(c)$, and it produces responses of the form \texttt{Decide}$(\sigma)$, where $\sigma$ is a c-struct. A c-struct set is a set, containing the element $\bot$, with an append operator $\bullet$ such that $\sigma \bullet c$ is a c-struct, for any c-struct $\sigma$ and command $c$. We say that two commands \textit{commute} when $\sigma\bullet c_1\bullet c_2 =  \sigma\bullet c_2\bullet c_1 $, for every c-struct $\sigma$. Intuitively, a c-struct represents a set of sequences that are all equivalent up to the ordering of commutative commands (see~\cite{lamport-generalized} for a complete discussion on c-struct). In the rest of the paper, unless otherwise specified, the symbol $c$, possibly sub-scripted, ranges over commands, and the symbol $\mathcal{D}$, possibly sub-scripted, ranges over sets of commands.

In the next sections we present our specification of leaderless generalized consensus algorithms, which is parameterized over a \textit{dependency-set} algorithm (\Cref{dep-algo}) and a \textit{map-agreement} algorithm (\Cref{map-algo}). 
%Processes proposals of commands to the \textit{Generalized Consensus} layer
%We also consider a deterministic state-machine $M$ whose set of commands is $C$. 
%We say that two commands $c_a$, $c_b$ \textit{commute} if executing $c_a$ before $c_b$ has the same effect on the state machine as executing $c_b$ before $c_a$. We assume that a command does not commute with itself.
%We also consider a symmetric relation $R \subseteq C\times C$, called \textit{dependency relation}, such that: for any command $c$, $\left( c,c \right)\notin R$, and if $\left( c_a,c_b \right)\notin R$ then $c_a$ and $c_b$ commute.

\subsection{Computing Dependency-Sets}
\label{dep-algo}

A dependency-set algorithm exposes the input interface $\texttt{announce}_p\left( c \right)$, where $c$ is a command, and the output interface $\texttt{suggest}_p \left( c,\mathcal{D}\right)$, where $p\in P$ is the process executing the call.  
Moreover, a dependency-set computation algorithm must ensure that:
\begin{enumerate}[noitemsep,nolistsep]
    \item For any suggestion ${suggest\left( c, d \right)}^p$, every command in $\{c\}\cup d$ must have been announced before.
    \item For any two suggestions ${suggest\left( c_1, d_1 \right)}^p$ and ${suggest\left( c_2, d_2 \right)}^p$,  if $c_1$ and $c_2$ do not commute (i.e., $\left( c_1,c_2 \right) \in R$) then either $c_1\in d_2$ or $c_2 \in d_1$.
\end{enumerate}

@@

\subsection{Agreeing on Dependency Sets}
\label{map-algo}
